---
title: "assignmentb4"
author: "Andras Szeitz"
date: "2023-11-27"
output: github_document
Roxygen: list(markdown = TRUE)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Option A -- Strings and functional programming in R

## Exercise 1 

I will employ the tidytext package and stop_words dataset to remove the most common stop words.

Installing the required packages.

```{r}

# install.packages("janeaustenr")
# install.packages("stringi")
# install.packages("stringi", dependencies = TRUE, type = "source")

```

Loading the necessary packages.

```{r}

library(janeaustenr)
library(stringi)
library(tidytext)
library(stringr)
library(tidytext)
library(dplyr)
library(ggplot2)

```

Selecting and loading the book titled Persuasion.

```{r}

text <- austen_books() %>%
  filter(book == "Persuasion")
head(text)

```

Breaking up the text into individual words.

```{r}

words <- text %>%
   unnest_tokens(word, text)
words

```

Remove the stop words using stop_words dataset.

```{r}

data("stop_words")
filtered_words <- words %>%
  anti_join(stop_words, by = "word")
filtered_words

```

Counting and sorting the words.

```{r}

word_counts <- filtered_words %>%
  count(word, sort = TRUE)
word_counts

```

Generating a lolly-pop plot for the top 20 most common words.

```{r}

# Assuming 'word_counts' is a data frame with 'word' and 'n' columns
top_words <- head(word_counts, 20)

# Create a lollipop plot
library(ggplot2)

ggplot(top_words, aes(x = reorder(word, n), y = n)) +
  geom_segment(aes(x = word, xend = word, y = 0, yend = n), color = "skyblue") +
  geom_point(color = "darkblue", size = 3) +
  labs(title = "Top 20 Most Common Words in 'Persuasion'",
       x = "Word",
       y = "Frequency") +
  theme_minimal() +
  coord_flip()

```

## Exercise 2

Making a function that converts words to my version of Pig Latin.

```{r}

#' Converting to Custom Pig Latin
#'
#' This function converts English words to my version of Pig Latin.
#' The rearrangement involves moving the first letter of the word to the end, #' and the last letter of the word to the beginning and adding "bla" to the
#' end.
#'
#' @param word A character string representing a single English word.
#' @return A character string of the word converted to custom Pig Latin.
#' @examples
#' custom_pig_latin("flower")
#' custom_pig_latin("summer")
#' custom_pig_latin("happy")
#' @export
custom_pig_latin <- function(word) {
  # Validating the input
  if (!is.character(word) || length(word) != 1) {
    stop("Input must be a single word (character string).")
  }

  if (nchar(word) == 0) {
    return("bla")
  }

  # Checking if word starts with a vowel
  if (tolower(substr(word, 1, 1)) %in% c('a', 'e', 'i', 'o', 'u')) {
    # Moving the last letter to the start and add "bla"
    return(paste0(substr(word, nchar(word), nchar(word)), substr(word, 1, nchar(word) - 1), "bla"))
  } else {
    # Moving the first letter to the end, then the last to the start, and add "bla"
    return(paste0(substr(word, nchar(word), nchar(word)), substr(word, 2, nchar(word) - 1), substr(word, 1, 1), "bla"))
  }
}

```

Presenting an example

```{r}
custom_pig_latin("flower") # "rlowefbla"
custom_pig_latin("summer") # "rummesbla"
custom_pig_latin("happy") # "yapphbla"
```

the test function

```{r}

library(testthat)

```

```{r}
# Begining test cases
test_that("Custom Pig Latin Conversion Works Correctly", {
  expect_equal(custom_pig_latin("flower"), "rlowefbla")
  expect_equal(custom_pig_latin("summer"), "rummesbla")
  expect_equal(custom_pig_latin("happy"), "yapphbla")
})

test_that("Handles Non-Standard Input", {
  expect_error(custom_pig_latin(123))
  expect_error(custom_pig_latin(TRUE))
  expect_error(custom_pig_latin(NULL))
})

test_that("Handles Empty and Single Character Strings", {
  expect_equal(custom_pig_latin(""), "bla")
  expect_equal(custom_pig_latin("a"), "abla")
})
```
