---
title: "assignmentb4"
author: "Andras Szeitz"
date: "2023-11-27"
output: github_document
Roxygen: list(markdown = TRUE)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Option A -- Strings and functional programming in R

## Exercise 1 

Using the tidytext package and stop_words dataset, I will remove the most common stop words from Jane Austen's Persuasion novel.

Installing the required packages.

```{r}

# install.packages("janeaustenr")
# install.packages("stringi")
# install.packages("stringi", dependencies = TRUE, type = "source")

```

Loading the necessary packages.

```{r}

library(janeaustenr)
library(stringi)
library(tidytext)
library(stringr)
library(tidytext)
library(dplyr)
library(ggplot2)

```

Selecting and loading the book titled Persuasion.

```{r}

text <- austen_books() %>%
  filter(book == "Persuasion")
head(text)

```

Breaking up the text into individual words.

```{r}

words <- text %>%
   unnest_tokens(word, text)
words

```

Remove the stop words using stop_words dataset.

```{r}

data("stop_words")
filtered_words <- words %>%
  anti_join(stop_words, by = "word")
filtered_words

```

Counting and sorting the words.

```{r}

word_counts <- filtered_words %>%
  count(word, sort = TRUE)
word_counts

```

Generating a lolly-pop plot for the top 20 most common words.

```{r}

# Assuming 'word_counts' is a data frame with 'word' and 'n' columns
top_words <- head(word_counts, 20)

# Create a lollipop plot
library(ggplot2)

ggplot(top_words, aes(x = reorder(word, n), y = n)) +
  geom_segment(aes(x = word, xend = word, y = 0, yend = n), color = "skyblue") +
  geom_point(color = "darkblue", size = 3) +
  labs(title = "Top 20 Most Common Words in 'Persuasion'",
       x = "Word",
       y = "Frequency") +
  theme_minimal() +
  coord_flip()

```

## Exercise 2

Making a function that converts words to my version of Pig Latin.

```{r}

#' Converting to Custom Pig Latin
#'
#' This function converts English words to my version of Pig Latin.
#' The rearrangement involves moving the first letter of the word to the end, #' and the last letter of the word to the beginning and adding "bla" to the
#' end.
#'
#' @param word A character string representing a single English word.
#' @return A character string of the word converted to custom Pig Latin.
#' @examples
#' custom_pig_latin("flower")
#' custom_pig_latin("summer")
#' custom_pig_latin("happy")
#' @export
custom_pig_latin <- function(word) {
  # Validating the input
  if (!is.character(word) || length(word) != 1) {
    stop("Input must be a single word (character string).")
  }

  if (nchar(word) == 0) {
    return("bla")
  }

  # Checking if word starts with a vowel
  if (tolower(substr(word, 1, 1)) %in% c('a', 'e', 'i', 'o', 'u')) {
    # Moving the last letter to the start and add "bla"
    return(paste0(substr(word, nchar(word), nchar(word)), substr(word, 1, nchar(word) - 1), "bla"))
  } else {
    # Moving the first letter to the end, then the last to the start, and add "bla"
    return(paste0(substr(word, nchar(word), nchar(word)), substr(word, 2, nchar(word) - 1), substr(word, 1, 1), "bla"))
  }
}

```

Presenting an example

```{r}
custom_pig_latin("flower") # "rlowefbla"
custom_pig_latin("summer") # "rummesbla"
custom_pig_latin("happy") # "yapphbla"
```

the test function

```{r}

library(testthat)

```

```{r}
# Begining test cases
test_that("Custom Pig Latin Conversion Works Correctly", {
  expect_equal(custom_pig_latin("flower"), "rlowefbla")
  expect_equal(custom_pig_latin("summer"), "rummesbla")
  expect_equal(custom_pig_latin("happy"), "yapphbla")
})

test_that("Handles Non-Standard Input", {
  expect_error(custom_pig_latin(123))
  expect_error(custom_pig_latin(TRUE))
  expect_error(custom_pig_latin(NULL))
})

test_that("Handles Empty and Single Character Strings", {
  expect_equal(custom_pig_latin(""), "bla")
  expect_equal(custom_pig_latin("a"), "abla")
})
```
## Exercise 3

Evaluating the mtcars dataset and fitting linear regression models for each car make to predict fuel efficiency (mpg) based on other variables.

```{r}

library(tidyverse)

# Load necessary packages
library(purrr)

# Load the mtcars dataset
data(mtcars)

# Task 1: Make a column of model objects
models <- mtcars %>%
  group_by(cyl) %>%
  nest() %>%
  mutate(model = map(data, ~ lm(mpg ~ disp + hp + wt, data = .)))

# Task 2: Evaluate the model (e.g., get residuals for each group)
models <- models %>%
  mutate(residuals = map2(model, data, ~ residuals(.x, data = .y)))

# Task 3: Print out intermediate tibble for inspection
print(models)

# Task 4: Unnest the resulting calculations
results <- models %>%
  unnest(cols = c(data, residuals)) %>%
  select(cyl, mpg, residuals)

# Task 5: Print your final tibble to screen
print(results)

# Task 6: Produce a plot communicating something about the result
results %>%
  ggplot(aes(x = residuals, y = mpg, color = as.factor(cyl))) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Residual Plot for Linear Regression Models by Cylinder",
       x = "Residuals",
       y = "Miles Per Gallon",
       color = "Cylinders")

```

Task 1: Grouped the mtcars dataset by the number of cylinders (cyl), then used nest() to create a nested column of data frames for each group. I used map() to fit a linear model (lm()) for each group.

Task 2: Used map2() to calculate residuals for each model, considering the original data.

Task 3: Printed out the intermediate tibble to inspect the fitted models and residuals for each group.

Task 4: Unnested the results, keeping the original data, and the residuals. This tibble is better for analysis and plotting.

Task 5: Print the final tibble to the screen.

Task 6: Produce a residual plot to visualize the fit and residuals for each group. The plot helps the reader to understand how well the linear model fits the data for each cylinder group.

The above example can be adapted to various datasets, providing a framework for fitting models, evaluating them, and visualizing the results for different groups in a dataset.

